---
title: "survmaximin"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{survmaximin}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To illustrate the usage of the SurvMaximin algorithm, first load in the simulated data, which includes a coefficient matrix derived locally from each source site and a varable covariance matrix from one target site. 

```{r setup}
library(SurvMaximin)
data(B_source); dim(B_source)
data(Sigma_target); dim(Sigma_target)
```

Then we fit the SurvMaximin model by calling the `survmaximin` function. Note that the $delta$ parameter controls the ridge penalty with the default value as 0. The transfer-learning coefficients are saved as `beta.est` in the output list. Weights for each source site are stored as `weight`, as well.

```{r}
output <- survmaximin(B_source, Sigma_target, delta=0.5)
output$beta.est
output$weight
```


To evaluate the performance of the SurvMaximin model, we first import the validation dataset.


```{r}
data(x.valid); length(x.valid)
data(z.valid); dim(z.valid)
data(delta.valid); length(delta.valid)
```
We can use `Est.Cval` function in the `survC1` package to calculate the C statistics from the validation data set and evaluate the model performance.

```{r}
valid.dat <- data.frame(`t_to_event_` = x.valid,
                        `death_ind` = delta.valid,
                        `score` = z.valid %*% output$beta.est)
c.maximin <- survC1::Est.Cval(valid.dat, tau = 5)$Dhat
c.maximin
```


If all sites can be treated as the target site and each site demands a SurvMaximin model to be fitted, then users can first store the locally estimated coefficients in one matrix ($p\times L$ where $L$ denotes the total number of sites), and data covariance matrices into a list：


```{r}
data(B_all); dim(B_all)
data(Sigma_all)
length(Sigma_all); dim(Sigma_all[[1]])

```
```{r}
output <- survmaximin_fed(B_all, Sigma_all, delta=0.5)
length(output)
output[[1]]$beta.est
output[[1]]$weight

```


To visualize the estimated results and inspect the sparsity of the estimators, we show the density plot for the survmaximin coefficient of each covariate from all sites as below. 

```{r fig.height=6, fig.width=7}
library(ggplot2)
beta.all = c()
p = 25; L = 16
for(i in 1:L){
  for(j in 1:p){
    beta.all = rbind(beta.all, 
                     data.frame(`variable` = paste0('covar',j), `site` = i, `maximin_coeff` = output[[i]]$beta.est[j]))
  }
}
beta.all$variable = factor(beta.all$variable, levels = paste0('covar', 1:25))

ggplot(beta.all, ggplot2::aes(x = maximin_coeff)) +
  geom_density() +
  xlim(c(-0.2, 0.2)) +
  geom_vline(xintercept = 0, col = 'red', linetype = 2) +
  facet_wrap(.~variable, scales = 'free_y')
```
